### 2015-03-18 evaluation.tex
update to table

@@

@@

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrr rr rr rr rr}
\centering
\input{experiments/tables/granularity.tex}
\end{tabular}
\caption{Results ...}
\label{tab:granularity}
\end{table*}

>>>>

\subsection{Experimental Setup}
\label{eval:setup}

We conducted all experiments on ... We use the following software versions: Z3 4.1; SMACK 1.4; Clang/LLVM 3.5; \corral commit 3aa62d7425b5; Boogie commit d6a7f2bd79c9.

\subsection{Benchmarks}
\label{eval:benchmarks}

We evaluate our methodology against 10 modules taken from the Linux kernel (currently a mix of latest and older distributions).

@@

We evaluate the scalability of our acceleration technique with respect to our benchmark sets.

@@

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrr rr rr r r}
\centering
\input{experiments/tables/granularity.tex}
\end{tabular}
\caption{Results ...}
\label{tab:granularity}
\end{table*}
